---
title: "Simulate from a fitted sam model"
author: "Mollie Brooks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
The most recent version of TMB includes the ability to simulated model, so we have implemented that ability in `stockassessment`. By default, these simulations are conditional on the estimated values of `F` and `N` but it is possible to also simulate `F` and `N` forward from the initial time point using the `sim.condRE` argument to the `sam.fit` function.

```{r setup, include=FALSE, message=FALSE}
library(stockassessment)
library(knitr)
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
```
Read in and organize the data using special fuctions

```{r data}
cn <- read.ices("nsher/cn.dat")
cw <- read.ices("nsher/cw.dat")
dw <- read.ices("nsher/dw.dat")
lf <- read.ices("nsher/lf.dat")
lw <- read.ices("nsher/lw.dat")
mo <- read.ices("nsher/mo.dat")
nm <- read.ices("nsher/nm.dat")
pf <- read.ices("nsher/pf.dat")
pm <- read.ices("nsher/pm.dat")
sw <- read.ices("nsher/sw.dat")
surveys <- read.ices("nsher/survey.dat")
dat <- setup.sam.data(surveys=surveys,
                    residual.fleet=cn, 
                    prop.mature=mo, 
                    stock.mean.weight=sw, 
                    catch.mean.weight=cw, 
                    dis.mean.weight=dw, 
                    land.mean.weight=lw,
                    prop.f=pf, 
                    prop.m=pm, 
                    natural.mortality=nm, 
                    land.frac=lf)

```

```{r conf}
conf <- defcon(dat)
conf$fbarRange <- c(2,6)
conf$corFlag <- 1
conf$keyLogFpar <- matrix(c(
-1,   -1,   -1,   -1,   -1,   -1,   -1,   -1,   -1,
-1,    0,    1,    2,    3,    4,    5,    6,   -1,
-1,    7,   -1,   -1,   -1,   -1,   -1,   -1,   -1,
 8,   -1,   -1,   -1,   -1,   -1,   -1,   -1,   -1), nrow=4, byrow=TRUE)
```

Set up initial values for the parameters.
```{r par}
par <- defpar(dat,conf)
par$logFpar <- rep(0,9)
```

Fit the model.
```{r run, results='hide'}
fit <- sam.fit(dat,conf,par)
```

Simulate from the fitted model and store the simulated observations into a new data set with the same structure as the original data.
```{r sim}
simdat <- dat
simdat$logobs <- simulate(fit)[[1]]$logobs
```

Fit the same model to the simulated data and compare the plot to the original data.
```{r plot, fig.width=7, results='hide'}
fit2 <- sam.fit(simdat, conf, par)
ssbplot(fit)
ssbplot(fit2)
fbarplot(fit)
fbarplot(fit2)
recplot(fit)
recplot(fit2)
```

